---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
### Importing packages
Here we also set sf_use_s2 to false, which is required to enable `sf::st_crop()`.
```{r}
library(sfRotate)

sf::sf_use_s2(FALSE)
```
### Import data from `rnaturalearth`.
```{r}
# import data
world <- rnaturalearth::ne_countries(scale="medium",returnclass="sf")

# Define an angle to use in matrix transformations.
angle_to_tilt <- pi/4
``` 

### Transforming data
We can use `crop_sf` to crop the data to an 8-sided shape with radius 40. We can center this crop around the point (0,30), and shear using the tilt angle. To line up the shear nicely, we can rotate using the half of the tilt angle. If we wanted to, we could also transpose the data vertically by 10, to raise it above any outline we define.

``` {r}
data <- world %>%
  crop_sf(n_vertices = 8,radius= 40,crop_center = c(0,30))%>%
  shear_data(shear_angle=angle_to_tilt)%>%
  rotate_data(rotate_angle=angle_to_tilt/2)#%>%
  #transpose_data(y_add = 10)
```

### Create an outline shape
```{r}
box_shape <- create_boundary_shape(vertices = 8, radius = 40)
```
If you want to transform this box shape, `sf` requires that you first cast it to geometry type `POINT`. We will recast after transformations.
``` {r}
outline <- box_shape %>%
  sf::st_cast("POINT") %>%
  # cast to point before making any changes
  shear_data(shear_angle=angle_to_tilt) %>%
  rotate_data(rotate_angle=angle_to_tilt/2) %>%
  dplyr::summarise(geometry=sf::st_combine(geometry)) %>%
  sf::st_cast("POLYGON")
```

### Plotting
We can plot this using `ggplot2`.
``` {r}
ggplot2::ggplot(data=data) +
  ggplot2::geom_sf(data = outline,fill="lightblue") +
  ggplot2::geom_sf(fill="lightgreen",colour="black") +
  # Below this is all styling
  ggplot2::theme(axis.title=ggplot2::element_blank(),
                 axis.ticks =ggplot2::element_blank() ,
                 axis.text =ggplot2::element_blank() ,
                 plot.background =ggplot2::element_blank(),
                 panel.background = ggplot2::element_blank()
                 )
```




